Why Donors Donate?

### 2020-09-14 analysis/05_market_simulator.Rmd
Added default choices for orgs to match excel simulator

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"))

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes (1)"))

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust (1)"))

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month (1)"))

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'))

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust (2)"))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month (2)'))

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes (2)"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month (3)"))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved (1)'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved (2)'))

selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member (1)'))

selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member (2)'))

selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"))

selectInput("p1_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"))

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"))

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'))

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

selectInput("p1_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"))

@@

selectInput("org1_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("ai_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

@@

selectInput("org2_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("gp_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("gp_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

@@

selectInput("org3_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("ox_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("ox_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

@@

selectInput("org4_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("rc_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("rc_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

>>>>

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"),
         selected = "At least once a day")

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"),
         selected = "Always")

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE,
         selected = c("TV", "Print", "Social media"))

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often")

#Fix
selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel")

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"),
         selected = "Somewhat liberal")

#Fix
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions ")

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree",),
         selected = "Strongly agree")

# Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month")

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"),
         selected = "Important")

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'),
         selected = 'Protestant')

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant")

#Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities")

#Fix
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month")

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499")

#Fix
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered")

#Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month")

# fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved")

#Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved")

#Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership")

#Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership")
#Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership")
#Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union")

#Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member")
# Fix
selectInput("p1_environmental_member",
         label = "Environmental Org. Membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization")
# Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership")
# Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member")

# Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization")
# Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization")

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Male")

selectInput("p1_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married")

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "2 year degree")

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'),
         selected = "More than median of $61,372")

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "White")

selectInput("p1_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"),
         selected = "Less than median age of 36")

@@

selectInput("org1_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross")

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Emergency response")

selectInput("ai_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency")

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability")

@@

selectInput("org2_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross")

selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Environment")

selectInput("gp_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency")

selectInput("gp_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability")

@@

selectInput("org3_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross")

selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Human rights")

selectInput("ox_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency")

selectInput("ox_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability")

@@

selectInput("org4_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross")

selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Refugee relief")

selectInput("rc_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency")

selectInput("rc_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability")
